---
title: "Credit Card Fraud Detection"
author: "Aman Sharma"
date: "2023-06-10"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Project Details: 

This is a Credit Card Fraud Detection project for **Codeclause**.
The dataset available on *Kaggle* has been collected and analysed during a research collaboration of Worldline and the Machine Learning Group of ULB (Université Libre de Bruxelles) on big data mining and fraud detection. 

### Loading Packages

```{r packages, warning=FALSE, results='hide', message=FALSE, echo=TRUE}

library(tidymodels)
library(corrplot)
library(caret)
library(rpart)
library(rpart.plot)
library(ggplot2)
library(pROC)
library(neuralnet)

```
### Importing Data and exploratory analysis
'Class' is the response variable and it takes value 1 in case of fraud and 0 otherwise. We have 492 frauds out of 284,807 transactions.
```{r data}
data<- read.csv("C:/Users/91835/Desktop/CodeClause_data/creditcard.csv")
data<-na.omit(data)
head(data)
summary(data)
dim(data)
data %>% 
  filter(Class==1) %>% 
  count()

```

### Observing Correlation
Visible correlation can be observed between V5, V6, V7 and Amount.

```{r corr, warning=FALSE}
new_data<- cor(data)
corrplot(new_data)
```

Plotting them together.
```{r}
df<-data %>% 
  select(Amount, V5, V6, V7)
dfframe<-data.frame(df)
dfplot <- dfframe %>% gather(key, value, -Amount)

ggplot(dfplot, mapping = aes(x = Amount, y = value, color = key) ) + geom_line()


```

### Modelling
Splitting the data to train and test sets.
In addition to use of different models, we have also plotted the ROC curve to measure the model accuracy. The ROC-Curves can be compared to choose the best model and subsequently using it to predict new data. 

```{r model}
set.seed(1234)
var_split <- initial_split(data, prop = .8)
train_data<- training(var_split)
test_data<- testing(var_split)
```

### Decision Tree model
Building a Decision Tree model and using ROC curve to determine accuracy.
```{r decision, warning=FALSE}

decisionTree_model <- rpart(Class ~ . ,train_data, method = "class")
predicted_decision <- predict(decisionTree_model, test_data, type = "class")
tail(predicted_decision)

rpart.plot(decisionTree_model)
#ROC
model= train(Class~., data=train_data, method="rpart")
var2<-scale(test_data)
var_predict<- predict(model, newdata = var2)
auc.gbm = roc(test_data$Class, var_predict, plot = TRUE, col = "blue")

```

### Logistic Model
Building Logistic Model with ROC curve.
```{r logistic, warning=FALSE}
Logistic_Model=glm(Class~.,train_data,family=binomial())
plot(Logistic_Model)

lr.predict <- predict(Logistic_Model,test_data, probability = TRUE)
#ROC TEST
auc.gbm = roc(test_data$Class, lr.predict, plot = TRUE, col = "blue")

```

### Neural Net Model
Building Neural Net Model with ROC curve.
```{r, warning=FALSE}
neural_model<- neuralnet(Class ~ ., data=train_data)
# plot(neural_model)

neural_predict<- predict(neural_model, newdata= scale(test_data))
auc.gbm<- roc(test_data$Class, neural_predict, plot=TRUE, col="blue")

```


